Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-29 paper/main.tex
include time point in comparison

\subsubsection{Direct Comparison}
\label{subsec:direct-comparison}
In the scenario where no cells divide during the observed interval, we can use our extraction
algorithm to obtain the position of the cells and then compare them directly to the positions
calculated from the computational results.
Each cell contains a collection of vertices.
Given $M$ cells with $N$ vertices each and dimension $d$, the total information can be stored in an
array $\nu_{i,j,k}$ of shape $(M,N,2)$.
Comparing the results of a simulation $\nu$ with experimental values $\tilde{\nu}$ is thus only a
matter of comparing two of these arrays within a suitable cost function~\cite{Wang2020}.
In our approach we utilize a least squares approach given by

\begin{equation}
    L_{\text{LS}}(\vec{x}, \vec{y})
        = \sum\limits_{i,j,k}|\nu_{i,j,k} - \tilde{\nu}_{i,j,k}|^2
\end{equation}

which minimizes the distance between the corresponding vertices.
One important detail is that the ordering of vertices must be identical in the numerical and
experimental values.

>>>>

\subsubsection{Direct Comparison}
\label{subsec:direct-comparison}
In the scenario where no cells divide during the observed interval, we can use our extraction
algorithm to obtain the position of the cells and then compare them directly to the positions
calculated from the computational results.
Each cell contains a collection of vertices.
Given $N_c$ cells with $N_v$ vertices in $d$ dimensions at $N_t$ time points, the total information
can be stored in an array $\nu_{i,j,k,l}$ of shape $(N_c,N_v,d,N_t)$.
Comparing the results of a simulation $\nu$ with experimental values $\tilde{\nu}$ is thus only a
matter of comparing two of these arrays within a suitable cost function~\cite{Wang2020}.
In our approach we utilize a least squares approach given by

\begin{equation}
    L_{\text{LS}}(\vec{x}, \vec{y})
        = \sum\limits_{i,j,k,l}|\nu_{i,j,k,l} - \tilde{\nu}_{i,j,k,l}|^2
\end{equation}

which minimizes the distance between the corresponding vertices at each time point.
One important detail is that the ordering of vertices must be identical in the numerical and
experimental values.
